CompDec - Detection of the Compression Algorithm of File Fragments using Convolutional Neural Networks

### 2021-01-08 paper/main.tex
Clarify hypothesis and the used sample of the database

@@

@@

The model was trained on 2 000 000 samples (250 000 samples per class) and tested using 200 000 samples (25 000 samples per class) (a rough 90\%/10\% split). The model was set to train for 100 epochs, based on the time required for each epoch and the time we could allocate for this procedure.

@@

@@

Future work could focus on developing a new purpose-built CNN. The model presented in this paper was initially built for general file fragment classification and was not adapted for compressed file fragment\cite{chen2018}. Another potential area of improvement would be exploring LSTMs. Using these networks could enable the model to learn longer distance relationships throughout the files, instead of the simpler patterns detected by CNNs\cite{LE2018S118}. Evaluating the accuracy after training the model using different optimizers and loss functions could have yielded better results. By conducting an experiment using different configurations, one could have found a better design.

>>>>

The hypotheses are:

\textbf{H$_1$}: The machine-learning system achieves an accuracy that is higher than that of random guesses.

\textbf{H$_0$}: The machine-learning system achieves an accuracy equivalent to random guesses.

@@

The accuracy of a random guess is defined to be $12.5\%$ as there are eight classes present in the dataset described in \ref{method:dataset}.

@@

Using the provided tools, all of the available threads of the GovDocs1 dataset were downloaded, compressed and indexed as chunks as mentioned in \ref{method:dataset}. The model was trained on 2 000 000 of these samples (250 000 samples per class) and tested using 200 000 of the samples (25 000 samples per class) (a rough 90\%/10\% split). The used seed for the sampling is $1.3035772690$. The model was set to train for 100 epochs, based on the time required for each epoch and the time we could allocate for this procedure.

@@

The accuracy of the trained model after five epochs was 41\%, thus proving the hypothesis that a machine-learning system can be used to achieve an accuracy higher than that of random guesses.

@@

Future work could focus on developing a new purpose-built CNN. The model presented in this paper was initially built for general file fragment classification and was not adapted for compressed file fragment\cite{chen2018}. Another potential improvement would be to train separate models for each class and combine them into a single system - thus potentially increasing the accuracy of some classes. Yet another potential area of improvement would be exploring LSTMs. Using these networks could enable the model to learn longer distance relationships throughout the files, instead of the simpler patterns detected by CNNs\cite{LE2018S118}. Evaluating the accuracy after training the model using different optimizers and loss functions could have yielded better results. By conducting an experiment using different configurations, one could have found a better design.
